%LaTeX Template for short student reports.
% Citations should be in bibtex format and go in references.bib
\documentclass[a4paper, 11pt]{article}
\usepackage[top=3cm, bottom=3cm, left = 2cm, right = 2cm]{geometry} 
\geometry{a4paper} 
\usepackage[utf8]{inputenc}
\usepackage{textcomp}
\usepackage{graphicx} 
\usepackage{amsmath,amsfonts,amssymb,amsthm}  
\usepackage{bm}  
\usepackage[backend=bibtex,style=numeric]{biblatex}  %backend=biber is 'better'
\usepackage[bookmarks,colorlinks,breaklinks]{hyperref}  
%\hypersetup{linkcolor=black,citecolor=black,filecolor=black,urlcolor=black} % black links, for printed output
\usepackage{memhfixc} 
\usepackage{pdfsync}  
\usepackage{fancyhdr}
\usepackage{array}
\usepackage[T1]{fontenc}
\usepackage{booktabs, multirow}
\usepackage[
singlelinecheck=false % <-- important
]{caption}
\usepackage{url}
\newcommand{\Lagr}{\mathcal{L}}
\newcommand{\Real}{\mathbb{R}}

\graphicspath{ {./images/} }

\pagestyle{fancy}

\renewcommand{\contentsname}{Rozdziały}
\renewcommand{\figurename}{Grafika}
\newtheorem{theorem}{Theorem}
\captionsetup[table]{name=Tabela}

\title{Manifolds}
%\date{}

\addbibresource{references.bib}

\begin{document}
\maketitle
\hypersetup{linkcolor=black}
\tableofcontents

\section{Topology}
TODO: add

\section{Tangent Space}

\subsection{Definition}
Let $(M, \tau)$ be a $C^k$ differentiable manifold, $(U, \phi)$ chart on $M$ and $p \in U$. 
Let $\gamma_1, \gamma_2: (-1, 1) \rightarrow U$ be two curves such that $\gamma_1(0) = \gamma_2(0) = p$ and $D_{\phi \circ \gamma_1}(x), D_{\phi \circ \gamma_2}(x) \in C^k[(-1, 1), R^n]$. \\
Let \texttildelow T be an equivalence relation on the set of curves meeting the above conditions s.t.
$\gamma_1 \text{\texttildelow} \gamma_2 \iff D_{\phi \circ \gamma_1}(\phi \circ \gamma_1)(0) = D_{\phi \circ \gamma_2}(\phi \circ \gamma_2)(0)$. \\
Finally, a tangent space $T_pM$ is defined as a set of equivalence classes of curves meeting the above conditions. \\
\begin{flalign}
	& [\gamma]_\text{\texttildelow} = \{\gamma': (-1, 1) \rightarrow U \text{ s.t. } \gamma \text{\texttildelow} \gamma' \}  \\
	& T_pM = \{[\gamma]_\text{\texttildelow}: (-1, 1) \rightarrow U, \phi \circ \gamma \in C^k[(-1, 1), \mathbb{R}^n], \gamma(0) = p \}
\end{flalign}
Since $\gamma_1(0) = \gamma_2(0) = p \implies D_{\phi \circ \gamma_1}(0) = D_{\phi \circ \gamma_2}(0) \iff [\gamma_1]_\text{\texttildelow} = [\gamma_2]_\text{\texttildelow}$, it follows that\\
SHOW INDEPENDENCE FROM CHART. \\

\subsection{Operations on tangent space}
To define operations on the elements of $T_pM$, if $(U, \phi)$ is a chart with $p \in U$, one may define a map:

\begin{flalign}
	& h_*: T_pM \rightarrow T_{\phi(p)}\mathbb{R}^n = \mathbb{R}^n, \\
	& h_*([\gamma]_\text{\texttildelow}) := D_{\phi \circ \gamma}(0). \\
\end{flalign}
Note that $D_{\phi \circ \gamma}(0)$ is a well defined $\phi \circ \gamma: \Real \rightarrow \Real^n$. \\
\\
Then the operations on $T_pM$ are defined as follows:
\begin{flalign}
	& \text{for } u, v \in T_pM \text{ and } \lambda \in \mathbb{R} \\
	& u + v := h_*^{-1}( h_*(u) + h_*(v) ), \\
	& \lambda v:= h_*^{-1}(\lambda h_*(v) ). \\
\end{flalign}
\subsubsection{Bijectivity} 
By the definition of a chart, it has to be a homeomorphism (continous, bijective) map.
Thus $T_pM$ is a vector space isomorphic to $\mathbb{R}^n$.

\subsubsection{Basis}
If $B = \{e_1, e_2, .. e_n\}$ is a basis of $\mathbb{R}^n$, then $B_{T_pM} = \{h_*^{-1}(e_1), h_*^{-1}(e_2), .. h_*^{-1}(e_n)\}$ is a basis of $T_pM$.


\subsection{Differential}

Let $(M_1, \tau_1) (M_2, \tau_2)$, be $C^k$ differentiable manifolds, $f: M_1 \rightarrow M_2$ be a smooth map and $p \in U \in \tau_1$. \\
We define a differential (or pushforward) as a map between tangent spaces as follows:
\begin{flalign}
	& df: T_pM_1 \rightarrow T_{f(p)}M_2 \\
	& df([\gamma]_\text{\texttildelow}) := [f \circ \gamma]\text{\texttildelow} \in T_{f(p)}M_2
\end{flalign}
Note that $[f \circ \gamma]\text{\texttildelow}$ is a equivalence class of all curves $f \circ \gamma: (-1, 1) \rightarrow M_2$, with $(f \circ \gamma)(0) = f(p)$ and $(f \circ \gamma_1) \text{\texttildelow} (f \circ \gamma_2) \iff D_{\psi \circ (f \circ \gamma_1)}(0) = D_{\psi \circ (f \circ \gamma_2)}(0)$, for some $\psi$ being a chart of $M_2$ on neighbourhood of $f(p)$.

\subsection{Cotangent Space}
Let $M$ be a $C^k$ differentiable manifold, $p \in M$. \\
If $T_pM$ is a tangent space, then its dual space $T_p^*M$ is called a cotangent space. \\

\subsubsection{Basis of Cotangent Space}
If $B_{T_pM} = \{b_1, b_2, ..., b_n\}$ is a basis of tangent space, then basis of its dual space $B^*_{T_p^*M} = \{b_1^*, b_2^*, ..., b_n^*\}$ can be found as follows:
\begin{flalign}
	& b_i^* \in \Lagr(T_pM \rightarrow \Real), b_j \in B_{T_pM} \\
	& b_i^* (b_j) := \delta_{ij} =
						\begin{cases}
								1, &         \text{if } i=j,\\
								0, &         \text{if } i\neq j.
						\end{cases}
\end{flalign}

\section{Submersion}
Let $M, N$ be manifolds and $f: M \rightarrow N$ be a smooth map. \\
Its pushforward $df: T_pM \rightarrow T_{f(p)}N$ is called an immersion if it is a bijective map. \\

\section{Tangent bundle}
Let $M$ be a $C^k$ differentiable manifold. We define a Tangent bundle as a set consisting of all tangent spaces defined as:
$TM := \bigcup\limits_{p \in M} \{p\} \times T_pM$

\subsubsection{Natural projection}
Natural projection $\pi: TM \rightarrow M$ is defined as:
$\pi(p, T_pM) := p$

\section{Metric Tensor}
Let M be a $C^k$ differentiable manifold and $p \in M$. \\
A metric tensor $g_p: T_pM \times T_pM \rightarrow \Real$ is a map that is: \\
\begin{itemize}
  \item Bilinear: 
		\begin{itemize}
			\item $g_p(u, \lambda v) = g_p(\lambda u, v) = \lambda g_p(u, v)$,
			\item $g_p(u + w, v) = g_p(u, v) + g_p(w, v)$,
			\item $g_p(u, v + w) = g_p(u, v) + g_p(u, w)$.
		\end{itemize}
  \item Symmetric: $g_p(u, v) = g_p(v, u)$.
  \item Nondegenerate:	$\forall v \in T_pM: v \neq 0 \implies \exists u \in T_pM: g_p(u, v) \neq 0$
  \item If $g_{u, v}: M \rightarrow \Real, \text{ with } g_{u, v}(p) := g_p(u, v)$, then \\
$g_{u, v}$ is a smooth function.
\end{itemize}

\section{Riemann semi-maniofld}
Let $M$ be a $C^k$ smooth manifold and $g_p: T_pM \times T_pM \rightarrow \Real$ be its metric tensor. We say that a tuple $(M, g_p)$ is called a Riemann semi-maniofld. \\
$g_p$ is also called a Riemann Metric.

\subsection{Riemann norm}
For a given metric tensor $g_p$, Riemann norm is defined as $\|\cdot\|: T_pM \rightarrow \Real, \text{ with } \|v\| := \sqrt{g_p(v, v)}$

\subsection{Curve length}
Let $\gamma: (a, b) \subseteq \Real \rightarrow M$ be a parametrized smooth map. \\
We define the length of this curve as: \\
$L(\gamma) := \int_a^b \|[\gamma]_\text{\texttildelow}\| dt = \int_a^b \sqrt{g_p([\gamma]_\text{\texttildelow}, [\gamma]_\text{\texttildelow})} dt$


\section{Exterior Algebra}
\subsection{Alternating bilinear form}
Let $V$ be a vector space over a field $F$. An alternating (or antisymmetric) bilinear form on $V$ is a bilinear form $B: V \times V \rightarrow F$ such that $B(v, w) = -B(w, v)$.

\subsection{Second exterior power}
Let $V$ be a finite-dimensional vector space over a field $F$ \\
and $V_B = \{ B: V \times V \rightarrow F : B \text{ is alternating bilinear form.} \}$ be a vector space of all alternating bilinear forms.
The second exterior power of $V$, denoted with $\bigwedge\nolimits^2 V$ is a dual space of $V_B$. i.e. $\bigwedge\nolimits^2 V = V_B^*$. Elements of $\bigwedge\nolimits^2 V$ are called 2-vectors.

\subsection{Exterior product}
Let $V$ be a finite-dimensional vector space over a field $F$ and $v, u \in V$ and $\bigwedge\nolimits^2 V$ be its second exterior power. Exterior product of $v$ and $u$, is a linear map to $F$ $v \wedge u \in \bigwedge\nolimits^2 V$ \\
$(v \wedge u)(B) = B(v, u)$. \\\\
From this definition, the following properties follow:
\begin{flalign}
	&(u \wedge v)(B) = B(u, v) = -(u \wedge v)(B) = -B(v, u) \\
	&(u \wedge u)(B) = -(u \wedge u)(B) = 0 \\
	&\text{if $\{v_1, v_2, \dots, v_n\}$ is a basis for $V$, then $\{ v_i \wedge v_j: i, j \in \{1, 2, \dots, n\}, i < j \}$ is a basis for $\bigwedge\nolimits^2 V$.}
\end{flalign}

\begin{theorem}
	$u, v \in V, u \neq 0 \implies (u \wedge v = 0 \iff \exists_{\lambda \in F}: v = \lambda u)$
	\begin{proof}
	This basically mean that $u, v$ are in the same subspace and this may be shown with the following. \\
	Let $v = \lambda u$. Then $u \wedge v = u \wedge (\lambda u) = \lambda (u \wedge u) = 0$. \\
	\end{proof}
\end{theorem}

%\section{Differential forms}
%
%\subsection{Tensor Product}
%Let $V$, $W$ be two vector spaces over a common field the respective bases $B_V = \{b_{v_1}, b_{v_2}, \dots\}, B_W = \{b_{w_1}, b_{w_2}, \dots\}$. A tensor product of these 2 vector spaces, denoted with $A \otimes B$ is a new vector space.
%A set of all the bases of this vector space is given by: $B = \{ (v, w) \in B_V \times B

\end{document}

